Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Jupiter-Sized Planet in IC~2602

### 2020-06-29 paper/ms.tex
update manuscript

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f2b.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{
    {\bf Photometry of \tn.} {\it Top:}
    Phase-folded TESS transit. Gray points are 2-minute PDCSAP flux
    measurements, detrended with a 0.3-day robust Huber spline (see
    Section~\ref{subsec:tess}).  Black points are binned to 6-minute
    intervals, and the errorbar shows the median uncertainty for the
    black points.  The gray line shows the median model corresponding
    to the combined TESS and ground-based transit fit
    (Table~\ref{tab:posterior}).  {\it Bottom:} Multicolor photometry from the El Sauce
    0.36m; gray points are binned to 10-minute intervals.  Models show
    $2\sigma$ lower limits on the transit depths in the Cousins-R and
    Johnson-B bandpasses used to rule out specific false positive
    scenarios (see Section~\ref{subsec:colorphot}).
    \label{fig:jointphot}
	}
\end{figure*}

@@

\paragraph{Custom aperture analysis}
Based solely on the TESS data, both Star A and Star B
were possible sources of blended eclipsing binary signals.
For instance, a 30\% eclipse of Star A could produce
dips with the correct depth ($\approx$0.4\%) to explain the \tn\ signal.
Star B is resolved in the ground-based images, while Star A is not.

To assess this possibility with the ground-based photometry, we
produced light curves centered on \tn\ with
circular apertures of radii ranging from 0.7$''$ to 5.1$''$.
We did not detect any statistically significant variation in the depth
of the transits with aperture size.
Two lines evidence rule out Star B as the eclipsing source:
first, the transits
were detected in the smallest apertures.
Second, we made light curves with $2.1''$ apertures centered on Star B,
and they did not show the transit.

To assess the possibility of Star A as the eclipsing body,
we created light curves with a custom set of circular apertures
with radii of $2.1''$ and positions ranging from Star A (2.3$''$ west of \tn) to 2.3$''$
east of \tn.  We did not detect any variation of the transit depth
along this line of light curves, as would be expected if Star A were
the eclipse host.  The apertures east of \tn\ are particularly
constraining, as they exclude over 90\% of the flux from Star A.
The eclipse on Star A would therefore need to be excessively deep to
produce the observed eclipse depth.
We take this as evidence that \tn\ is the source of the transit signal
to within $\approx2.0''$.

@@

Validating a transiting planet means statistically arguing that
the data are much more likely to be caused by a planet than by other
astrophysical false positives. The concept of validation has been
developed and calibrated by {\it e.g.},
\citet{torres_modeling_2011,morton_efficient_2012,diaz_pastis_2014,santerne_pastis_2015,morton_false_2016}
and \citet{giacalone_triceratops_2020}.  ``Validation'' is different
from ``confirmation'', which means that there is overwhelming evidence
that the data must be explained by a planet, for instance through
combined photometric transits and a radial velocity mass measurement.

Assuming the eclipse is localized to the target star, potential false positive scenarios
include eclipses of a background binary (BEB), eclipses of a
hierarchical system bound to the primary star (HEB), and the possibility
that the eclipses are simply caused by a stellar companion,
rather than a planetary one (EB).

Figure~\ref{fig:fpscenario} provides a visual summary of the possible
astrophysical false positive scenarios, as well as our ability to rule
them out based on our combined photometry, velocimetry, and imaging.
We proceed by describing each constraint in detail, and then present a
statistical calculation using \texttt{VESPA}
\citep{morton_efficient_2012} to demonstrate that the probability \tn\
is an astrophysical false positive is small enough to consider it
validated.

@@

\subsubsection{Transit Depth}
In HEB and BEB scenarios, the flux from \tn\ and the true eclipsing
binary host would blend together, reducing the ``true'' eclipse depth
$\delta_{\rm true}$ to produce the observed depth
$\delta_{\rm obs}$:
\begin{equation}
  \delta_{\rm obs}
  = 
  \delta_{\rm true} \frac{F_{\rm neighbor}}{F_{\rm total}},
\end{equation}
where the total flux and the flux from the neighbor are labelled as
such.  The requirement that the eclipse is produced by stars and that
$\delta_{\rm true} < 0.5$ translates to a bound on the faintest
possible blended companion stars:
\begin{equation}
  \Delta m < -\frac{5}{2} \log_{10} \left( \frac{0.5}{\delta_{\rm obs}} \right).
\end{equation}
For \tn\ ($T=9.93$), this implies that any stellar companion invoked
to explain the transit depth must be brighter than $T=15.07$.  In
Figure~\ref{fig:fpscenario}, we set the spatial limit to 2$''$ based
on the precision at which we have localized the transits using
seeing-limited ground-based photometry.

For box-shaped transits, this argument can be
extended to even more restrictive depths \citep[{\it
e.g.},][]{seager_unique_2003,vanderburg_hr858_2019,rizzuto_tess_2020}
However, since the transits of \tn\ are grazing, the second and third
contact points do not occur, and the shape of the transit is not
restrictive.

\subsubsection{Speckle Imaging}
The contrast limits obtained through the SOAR $I$-band speckle imaging
(Section~\ref{subsec:speckle}) are shown in
Figure~\ref{fig:fpscenario}.  While ``Star A'' was detected in the
SOAR images, our ground-based photometry rules it out as a possible
source of the eclipse signal (Section~\ref{subsec:groundphot}).  To
convert the remaining contrast constraints to limits on the masses of
possible bound companions, we used the
\citet{baraffe_evolutionary_2003} models for sub-stellar mass objects
and the MIST isochrones for stellar mass objects
\citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015,dotter_mesa_2016,choi_mesa_2016}.
We assumed that the system age was 35 Myr, to ensure that companions
would be at a plausible state of contraction.

To convert from theoretical effective temperatures and bolometric
luminosities to expected magnitudes in instrumental bandpasses, we
assumed that all soruces had blackbody spectra.  While this is
a simplification, the custom instrumental bandpasses prevented a fully
consistent stellar evolutionary calculation.  Using the theoretical
stellar parameters and the measured transmission functions
\citep{tokovinin_ten_2018}, we then calculated the apparent magnitudes
of stellar companions of different masses, and interpolated
to produce the scale shown on the upper-right in
Figure~\ref{fig:fpscenario}.

\subsubsection{Not SB2}
As described in Section~\ref{subsec:chiron}, we searched the CCFs of
the CHIRON spectra to determine whether \tn\ is double-lined.  For a
stellar companion well-separated in velocity, this typically shows
companions with flux-fractions $F_2/F_1 \gtrsim 2\%$.  For plotting
purposes, in Figure~\ref{fig:fpscenario} we have assumed a
flux-fraction limit of 5\% ($\Delta {\rm mag} \approx 3.25$).

\subsubsection{RVs}
The combined radial velocities from FEROS, CHIRON, and Veloce can be
used to place limits on the presence of massive, close-in bound
companion to \tn.  We derived the relevant limits using
\texttt{radvel} \citep{fulton_radvel_2018}.  We assumed circular
orbits for the companion, and then performed two sets of fits.

% timmy.drivers.oneoff_drivers.get_mass_upper_limit
For the first fit, we assumed a restrictive prior on the period and
time of periapse, using the known ephemeris from the transit.  We then
fitted for the period, time of periapse, semi-amplitude, instrument
offsets, and jitter parameters.  This yielded a non-detection of the
planet's orbit.  The corresponding 3-$\sigma$ (99.7$^{\rm th}$
percentile) upper limit on $M_{\rm p} \sin i$ is $1.20 M_{\rm Jup}$.
The data and corresponding model are shown in Figure~\ref{fig:rvs}.

The above exercise rules out the possibility that the observed
eclipses are caused by a star orbiting \tn.  The lack of a linear
trend in the radial velocities, particularly in the FEROS data, can be
used to further limit the presence of a hierarchical binary system.
To constrain this second possibility, we placed a wide log-uniform
prior on the semi-amplitude and period ($\log K\ [{\rm m\,s^{-1}}]
\sim \mathcal{U}(1,10^5)$, $\log P\ [{\rm days}] \sim \mathcal{U}(0.1,
10^{15})$).  We then fitted again for the semi-amplitude, period, time
of conjunction, instrument offsets, and jitter parameters.  We
converted the resulting posterior in period and semi-amplitude to
minimum mass and semi-major axis assuming Kepler's third law.  The
resulting $3\sigma$ limits are shown in Figure~\ref{fig:fpscenario}.

\subsubsection{Multicolor Photometry}
\label{subsec:colorphot}
% TODO: this section is ridiculously long. Abbreviate to 2 paragraphs, 3
% at most.

HEB and to a lesser extent BEB scenarios can be limited
by color photometry.
In the absense of color photometry, the most plausible HEB scenarios for TOI
837 involve pairs of eclipsing M dwarfs (Figure~\ref{fig:fpscenario}).
These eclipses are redder than eclipses of the G0V \tn.
Observations that the transit depth does not decrease
going to blue bands can therefore rule out these scenarios.

\paragraph{Simple Example}
% SEE June 1, 2020 email in "Re: TOI-837.01" thread
As a simple example, assume $M_2=M_3=0.2M_\odot$ in a twin HEB.
Assume PMS evolution, and
use MIST isochrones for a 35 Myr system to convert between stellar properties. 
Take transmission functions (filters only; no instrument or atmosphere
response) from the SVO filter profile service\footnote{\url{http://svo2.cab.inta-csic.es/theory/fps/}}.
Integrate up blackbody functions over each bandpass for each star, and
get estimates of the eclipse depths if there were a total eclipse (of
either of the secondary or tertiary) with this set of parameters.  The
apparent eclipse depths in various Bessel and Cousins bandpasses are:
\begin{align}
%FIXME: check these numbers
  \delta_{\rm U_B} &= 5.03\times10^{-4} \ ({\rm Bessel\ U})\nonumber \\
  \delta_{\rm B_B} &= 1.39\times10^{-3}\ ({\rm Bessel\ B})\nonumber \\
  \delta_{\rm V_B} &= 3.31\times10^{-3}\ ({\rm Bessel\ V})\nonumber \\
  \delta_{\rm R_C} &= 5.59\times10^{-3}\ ({\rm Cousins\ R})\nonumber \\
  \delta_{\rm I_C} &= 9.69\times10^{-3}\ ({\rm Cousins\ I})\nonumber \\
  \delta_{\rm T}   &= 9.18\times10^{-3}\ ({\rm TESS})
\end{align}

Our chief interest is the relative depths, because geometry lets all the
depths be scaled to match the observed TESS depth of $\approx$43 ppt.
(In this case, all depths would be scaled down by a multiplicative factor of
2.1).

The crucial point is that the bluest bands--- U and B---are roughly 10
times shallower than TESS-band, because the M dwarf blackbody function
turns over at 2 times longer wavelengths than the G dwarf blackbody
(Wien's law).

Therefore if TOI 837 were a hierarchical eclipsing M dwarf pair,
Phil's two R-band observations should have shown eclipses a factor of
1.64x shallower than TESS observed (so, 24ppt, instead of the ~40ppt
observed). So, the 40 (+/- 10ish) ppt R-band depths seen in Phil's
transits vs TESS-band argue for a planet, but the level of confidence
could probably be improved with U or B.

\paragraph{Limits on Masses of Bound Companions}

With this intuition in place, we derived the limits on masses of bound
hierarchical eclipsing companions as follows.  We assumed that each
system was composed of the primary (\tn), plus a tertiary companion
eclipsing a secondary companion every 8.3 days.

For secondary masses ranging from 0.07 to 1.10 $M_\odot$, and
mass ratios ($M_3/M_2$) from 0.1 to 1, we then 
calculated the observed maximal eclipse depth of Star 3 in front of
Star 2 in a number of bandpasses.
As before, we interpolated between mass, effective temperature, and radius
assuming the MIST isochrones for a 35$\,$Myr old system,
and also assumed that each source had a blackbody spectrum.

We excluded systems for which the maximal eclipse depth in TESS-band
was less than the observed depth ({\it i.e.}, systems for which the tertiary
was too small).
For the systems with maximal eclipse depths in TESS-band greater than
the observed TESS-band depth, we then calculated the multiplicative
factor required to shrink the depth (from the $b=0$ case) to match the
observed eclipse depth in the TESS-band.
We then scaled the depths in each of the other bandpasses by this
fixed geometric factor.

We then asked: given a fixed secondary mass, are there any tertiary
companions for which the expected $\delta_{\rm R_C}$ is larger than
the observed Rc-band depth?
In cases for which the answer was yes, we could not rule out such
hierarchical eclipsing binary systems.
Conversely, we were able to rule out systems
for which at fixed secondary mass no tertiary mass would
enable eclipses (in ${\rm R_C}$-band) of the necessary depth.

%FIXME FIXME
For a lower limit on $\delta_{\rm R_C}$ of 30$\,$ppt,
we found that the transition between systems that would produce
eclipses that no matter what were ``too red'', and systems that would
produce eclipses that could be sufficiently blue happens in \tn\ (for
${\rm R_C}$-band) at 0.38$M_\odot$.
The corresponding limit is shown in Figure~\ref{fig:fpscenario}.
For a $\delta_{\rm B_J}$ limit of 30$\,$ppt, the corresponding mass
limit is 0.82$M_\odot$.

\paragraph{Limits on Masses of Projected Companions}

Ignoring the effects of interstellar reddening,
the constraint that $M_2 \gtrsim 0.54 M_\odot$ based on
colors applies to background eclipsing binaries as well.
However, the blue eclipses produced by such systems ({\it e.g.}, a background G2V+K6V binary)
can be kept while making the systems fainter by moving them to greater
distances.
The only way to definitively rule out such scenarios is to 
prove that the loss of light is from the target star,
for instance by detecting the Rossiter-McLaughlin effect
during a transit.

Such scenarios are somewhat contrived in that since 
no secondary eclipse is observed, they require either
eccentric orbits to avoid secondary eclipses, or else a
background twin binary system at double
the orbital period.

@@

To derive physical parameters of \pn\ based on the photometry, we
fitted the TESS and ground-based transits simultaneously.

@@

>>>>

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f2b.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{
    {\bf Photometry of \tn.} {\it Top:}
    Phase-folded TESS transit. Gray points are 2-minute PDCSAP flux
    measurements, detrended with a 0.3-day robust Huber spline (see
    Section~\ref{subsec:tess}).  Black points are binned to 6-minute
    intervals, and the error-bar shows the median uncertainty for the
    black points.  The gray line shows the median model corresponding
    to the combined TESS and ground-based transit fit
    (Table~\ref{tab:posterior}).  {\it Bottom:} Multicolor photometry from the El Sauce
    0.36m; gray points are binned to 10-minute intervals.  Models show
    $2\sigma$ lower limits on the transit depths in the Cousins-R and
    Johnson-B bandpasses used to rule out specific false positive
    scenarios (see Section~\ref{subsec:colorphot}).
    \label{fig:jointphot}
	}
\end{figure*}

@@

\paragraph{Custom aperture analysis}
Based solely on the TESS data, both Star A and Star B
were possible sources of blended eclipsing binary signals.
For instance, a 30\% eclipse of Star A could produce
dips with the correct depth ($\approx$0.4\%) to explain the \tn\ signal.
Star B is resolved in the ground-based images; Star A is not.

To rule out blend scenarios with the ground-based photometry, we
produced light curves centered on \tn\ with
circular apertures of radii ranging from 0.7$''$ to 5.1$''$.
We did not detect any statistically significant variation in the depth
of the transits with aperture size.
Two lines of evidence rule out Star B as the eclipsing source:
first, the transits
were detected in the smallest apertures.
Second, we made light curves with $2.1''$ apertures centered on Star B,
and they did not show the transit.

To assess the possibility that Star A is the eclipsing body,
we created light curves with a custom set of circular apertures
with radii of $2.1''$ and positions ranging from Star A (2.3$''$ west of \tn) to 2.3$''$
east of \tn.  We did not detect any variation of the transit depth
along this line of light curves, as would be expected if Star A were
the eclipse host.  The apertures east of \tn\ exclude over 90\% of the flux from Star A.
The eclipse on Star A would therefore need to be excessively deep to
produce the observed eclipse depth.
We take this as evidence that \tn\ is the source of the transit signal
to within $\approx2.0''$.

@@

Validating a transiting planet means statistically arguing that the
data are much more likely to be explained by a planet than by an
astrophysical false positive. The concept of validation has been
developed and calibrated by {\it e.g.},
\citet{torres_modeling_2011,morton_efficient_2012,diaz_pastis_2014,santerne_pastis_2015,morton_false_2016}
and \citet{giacalone_triceratops_2020}.  ``Validation'' is different
from ``confirmation'', which means that there is overwhelming evidence
that the data {\it must} be explained by a planet, for instance
through combined photometric transits and a radial velocity mass
measurement.

Assuming an eclipse has been localized to the target star, potential
false positive scenarios include eclipses of a background binary
(BEB), eclipses of a hierarchical system bound to the primary star
(HEB), and the possibility that the eclipses are simply caused by a
stellar companion, rather than a planetary one (EB).

Figure~\ref{fig:fpscenario} provides a visual summary of the possible
astrophysical false positive scenarios, as well as our ability to rule
them out based on our combined photometry, velocimetry, and imaging.
In this Section we describe each constraint in turn, and then present a
calculation using \texttt{VESPA} \citep{morton_efficient_2012} to
demonstrate that the probability \tn\ is an astrophysical false
positive is small enough to formally validate it as a planet.

@@

\subsubsection{Transit Depth}
In HEB and BEB scenarios, the flux from \tn\ and the true eclipsing
binary host blend together, and reduce the ``true'' eclipse depth
$\delta_{\rm true}$ to the observed depth
$\delta_{\rm obs}$:
\begin{equation}
  \delta_{\rm obs}
  = 
  \delta_{\rm true} \frac{F_{\rm comp}}{F_{\rm total}},
\end{equation}
where the total system flux and the flux from only the companion
(``comp'') binary are labeled appropriately.  The requirement that the
eclipse is produced by stars and that $\delta_{\rm true} < 0.5$
translates to a bound on the faintest possible blended companion
system:
\begin{equation}
  \Delta m < -\frac{5}{2} \log_{10}
             \left( \frac{0.5}{\delta_{\rm obs}} \right).
\end{equation}
For \tn\ ($T=9.93$), this implies that any stellar companion invoked
to explain the transit depth must be brighter than $T=15.07$.  In
Figure~\ref{fig:fpscenario}, we set the spatial limit to 2$''$ based
on the precision at which we have localized the transits using
seeing-limited ground-based photometry.

If the transit were box-shaped, this argument could be extended to
even more restrictive depths \citep[{\it
e.g.},][]{seager_unique_2003,vanderburg_hr858_2019,rizzuto_tess_2020}
However, since the transits of \tn\ are grazing, the second and third
contact points do not occur, and the shape of the transit is not
restrictive.

\subsubsection{Speckle Imaging}
The contrast limits obtained through the SOAR $I$-band speckle imaging
(Section~\ref{subsec:speckle}) are shown in
Figure~\ref{fig:fpscenario}.  While ``Star A'' was detected in the
SOAR images, our ground-based photometry rules it out as a possible
source of the eclipse signal (Section~\ref{subsec:groundphot}).  To
convert the remaining contrast constraints to limits on the masses of
bound companions, we used the \citet{baraffe_evolutionary_2003} models
for sub-stellar mass objects and the MIST models for stellar mass
objects
\citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015,dotter_mesa_2016,choi_mesa_2016}.
We assumed that the system age was 35 Myr, so that companions would be
at a plausible state of contraction.

To convert from theoretical effective temperatures and bolometric
luminosities to expected magnitudes in instrumental bandpasses, we
made the simplying assumption that all sources had blackbody spectra.
Using the theoretical stellar parameters and the measured transmission
functions \citep{tokovinin_ten_2018}, we then calculated the apparent
magnitudes of stellar companions of different masses, and interpolated
to produce the scale shown on the upper-right in
Figure~\ref{fig:fpscenario}.

\subsubsection{Not SB2}
As described in Section~\ref{subsec:chiron}, we searched the CCFs of
the CHIRON spectra to determine whether \tn\ is double-lined.  For a
stellar companion well-separated in velocity, this typically reveals
companions with flux-fractions $F_2/F_1 \gtrsim 2\%$.  For plotting
purposes, in Figure~\ref{fig:fpscenario} we have assumed a
flux-fraction limit of 5\% ($\Delta {\rm mag} \approx 3.25$).

\subsubsection{RVs}
The combined radial velocities from FEROS, CHIRON, and Veloce can be
used to place limits on the presence of massive, close-in bound
companion to \tn.  We derived the relevant limits using
\texttt{radvel} \citep{fulton_radvel_2018}.  We assumed circular
orbits for the companion, and performed two sets of fits.

% timmy.drivers.oneoff_drivers.get_mass_upper_limit
For the first fit, we assumed a restrictive prior on the period and
time of periapse, using the known ephemeris from the transit.  We then
fitted for the semi-amplitude, instrument offsets, and jitter
parameters.  This yielded a non-detection of the planet's orbit.  The
corresponding 3-$\sigma$ (99.7$^{\rm th}$ percentile) upper limit on
$M_{\rm p} \sin i$ is $1.20 M_{\rm Jup}$.  The data and corresponding
model are shown in Figure~\ref{fig:rvs}.

The above exercise ruled out the possibility that the observed
eclipses are caused by a stellar-mass object orbiting \tn.  The lack
of a linear trend in the radial velocities, particularly in the FEROS
data, further constrains the presence of a hierarchical binary system.
To derive limits for this second possibility, we placed a wide
log-uniform prior on the semi-amplitude and period ($\log K\ [{\rm
m\,s^{-1}}] \sim \mathcal{U}(1,10^5)$, $\log P\ [{\rm days}] \sim
\mathcal{U}(0.1, 10^{15})$).  We then fitted for the semi-amplitude,
period, time of conjunction, instrument offsets, and jitter
parameters.  We converted the resulting posterior in period and
semi-amplitude to minimum mass and semi-major axis assuming Kepler's
third law.  The resulting $3\sigma$ limits are shown in
Figure~\ref{fig:fpscenario}.

\subsubsection{Multicolor Photometry}
\label{subsec:colorphot}

\paragraph{Multicolor photometry and HEB scenarios}
The most plausible HEB scenarios for \tn\ involve pairs of eclipsing M
dwarfs (Figure~\ref{fig:fpscenario}).  Eclipses of such stars are much
redder than eclipses of the G-dwarf \tn.  Limits on whether the
transit depth decreases in bluer bandpasses can therefore rule out
some HEB scenarios.

We fitted for the observed depths in different bandpasses using a
similar machinery as described in Section~\ref{subsec:planet}.  We fitted
each ground-based transit individually for the planet-to-star size
ratio, the impact parameter, and a local quadratic trend (the
ephemeris was assumed from an initial fit of only the TESS data).  The
corresponding $2$-$\sigma$ limits on the transit depths in Cousins-R
and Johnson-B band light curves were 2.82 and 1.77$\,$ppt,
respectively, and are shown in
Figure~\ref{fig:jointphot}.  Particularly in our Johnson-B light
curve, the transit depth is correlated with the mean and linear slope
of the light curve: a smaller depth is allowed if the data are fitted
with a larger linear slope and a larger mean.  Our quoted limits
marginalize over these correlations, and the depth measurement itself
is nearly Gaussian.

To determine what classes of HEB are eliminated by these limits, we
performed the following calculation.  We assumed that each system was
composed of the primary (\tn), plus a tertiary companion eclipsing a
secondary companion every 8.3 days.  For secondary masses ranging from
0.07 to 1.10 $M_\odot$, and mass ratios ($M_3/M_2$) from 0.1 to 1, we
then calculated the observed maximal eclipse depth caused by Star 3
eclipsing Star 2 in each observed bandpass.  As before, we
interpolated between mass, effective temperature, and radius assuming
the MIST isochrones for a 35$\,$Myr old system, and also assumed that
each source had a blackbody spectrum.  We used the transmission
functions from the SVO filter profile
service\footnote{\url{http://svo2.cab.inta-csic.es/theory/fps/}}.  For
a typical HEB system ({\it e.g.}, $M_2=M_3=0.2M_\odot$), the bluest
optical bandpasses produced eclipses roughly 10 times shallower than
in TESS-band, because the M-dwarf blackbody function turns over at
much redder wavelengths than the G-dwarf blackbody (Wien's law).

For a fixed secondary mass, we then asked whether any tertiary
companions existed for which the maximal expected eclipse depth could have
been larger than the observed depth.  In cases for which the answer
was yes, we could not rule out such hierarchical eclipsing binary
systems.  Conversely, we were ruled out systems for which at fixed
secondary mass no tertiary mass could enable eclipses of the necessary
depth (in ${\rm R_C}$-band, or in ${\rm B_J}$-band).
The ${\rm R_C}$-band limit corresponded to a secondary mass limit of 
$M_2 > 0.27 M_\odot$, and the ${\rm B_J}$-band corresponded to a
stronger limit of $M_2 > 0.70 M_\odot$.

\paragraph{Multicolor photometry and BEB scenarios}

While the above constraints rule out HEBs, certain configurations of BEB systems 
({\it e.g.}, a background G2V+K6V binary)
can produce blue eclipses while remaining undetected along the line of
sight.  Such scenarios are constrained by the lack of an observed
secondary eclipse, and therefore require either eccentric orbits to
avoid secondary eclipses, or else a background twin binary system at
double the orbital period.  The only way to definitively rule out such
scenarios is to prove that the loss of light is from the target star,
for instance by detecting the Rossiter-McLaughlin effect during a
transit.

@@

We derived physical parameters of \pn\ based on the photometry, we
fitted the TESS and ground-based transits simultaneously.
We trimmed the data to

@@

\subsubsection{multicolor transit fits}
Single transit at a time, with limited
